Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-17 ms.tex
added NSF GRF grant number
mask CO emission in f1 map figure, and explain this in the caption

\subsection{Molecular Emission}
Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
able to discard the relatively small number of frequency intervals contaminated
by strong molecular line emission. Unfortunately, while the \PLANCK~data 
considered in this study are of high angular resolution, the broad 
\PLANCK~bandpasses do not allow us to adopt the same approach as FDS99 in 
dealing with line emission. Instead, we must subtract estimates of the 
molecular line contamination from each \PLANCK~band in order to best isolate 
the thermal continuum we wish to characterize. The most prominent molecular 
line emission in the \PLANCK~bands of interest arises from the three lowest CO 
rotational transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 
GHz and J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 
217 and 353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
\PLANCK~143 GHz, but at a negligible level, $\sim$1000$\times$ fainter relative
to the dust continuum than J=1$\rightarrow$0 at 100 GHz.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
low-resolution fit in which $f_1$ is allowed to vary spatially.}
\end{center}
\end{figure}

@@

This material is based upon work supported by the National Science Foundation 
Graduate Research Fellowship under Grant No. We acknowledge support of NASA 
grant NNX12AE08G for this research. Based on observations obtained with Planck 
(http://www.esa.int/Planck), an ESA science mission with instruments and 
contributions directly funded by ESA Member States, NASA, and Canada. This 
research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard. \footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}

>>>>

\subsection{Molecular Emission}
\label{sec:mole}
Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
able to discard the relatively small number of frequency intervals contaminated
by strong molecular line emission. Unfortunately, while the \PLANCK~data 
considered in this study are of high angular resolution, the broad 
\PLANCK~bandpasses do not allow us to adopt the same approach as FDS99 in 
dealing with line emission. Instead, we must subtract estimates of the 
molecular line contamination from each \PLANCK~band in order to best isolate 
the thermal continuum we wish to characterize. The most prominent molecular 
line emission in the \PLANCK~bands of interest arises from the three lowest CO 
rotational transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 
GHz and J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 
217 and 353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
\PLANCK~143 GHz, but at a negligible level, $\sim$1000$\times$ fainter relative
to the dust continuum than J=1$\rightarrow$0 at 100 GHz.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
low-resolution fit in which $f_1$ is allowed to vary spatially. Red coloring
masks pixels with appreciable molecular emission, as defined in 
$\S$\ref{sec:mole}. Such pixels should not be trusted in this analysis, which 
is sensitive to the SED shape at low frequencies that are contaminated by CO 
line emission.}
\end{center}
\end{figure}

@@

This material is based upon work supported by the National Science Foundation 
Graduate Research Fellowship under Grant No. DGE1144152. We acknowledge support
of NASA grant NNX12AE08G for this research. Based on observations obtained with
Planck (http://www.esa.int/Planck), an ESA science mission with instruments and
contributions directly funded by ESA Member States, NASA, and Canada. This 
research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard. \footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}
